A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-25 doc/paper1-submission/paper5-adjusted.tex
Convert Figures 9 and 10.

\begin{figure}
\hfill{}\subfloat[Solution to subproblem \emph{ABCD}]{\includegraphics[scale=0.55]{Figures__subproblem_solutions__ott14\lyxdot tre}

}\hfill{}\subfloat[Solution to subproblem \emph{root}]{\includegraphics[scale=0.55]{Figures__subproblem_solutions__ott17\lyxdot tre}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Figures__grafted_solution__grafted_solution_ottnames\lyxdot tre}
\par\end{centering}
\caption{Grafted solution produced from the subproblems from
Fig. \ref{fig:subproblem-solutions.} and which is the 
backbone onto which taxa that are not included in any phylogeny
will be placed.
In a real analysis, the tips shown as E and F here
would be monotypic taxa (with children E1 and F1, respectively)
from the trivial subproblems that were omitted from from Fig. \ref{fig:subproblems-example}.}
\label{fig:grafted-solution}
\end{figure}

>>>>

\begin{figure}
\hfill{}\subfloat[Solution to subproblem \emph{ABCD}]{\includegraphics[scale=0.55]{Fig9a}

}\hfill{}\subfloat[Solution to subproblem \emph{root}]{\includegraphics[scale=0.55]{Fig9b}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Fig10.pdf}
\par\end{centering}
\caption{Grafted solution produced from the subproblems from
Fig. \ref{fig:subproblem-solutions.} and which is the 
backbone onto which taxa that are not included in any phylogeny
will be placed.
In a real analysis, the tips shown as E and F here
would be monotypic taxa (with children E1 and F1, respectively)
from the trivial subproblems that were omitted from from Fig. \ref{fig:subproblems-example}.}
\label{fig:grafted-solution}
\end{figure}
